The K2 Bright Star Survey

### 2019-05-06 paper/ms.tex
rearrange and rephrase a bit

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}. Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star. This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}. In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo. It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.

@@

This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

@@

% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.

>>>>

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}. Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star. This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}. In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo. It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry. 
% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.

@@

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

@@

Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm. The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.
